### 2015-02-02 paper/experiments.tex
results for experiment 2 take 2, some paper edits

We consider a medium sized network and the following scenarios
\begin{itemize}
\item \textbf{???} ($N=375$):
\item \textbf{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
\end{itemize}

>>>>

We consider a medium sized network based off of the I-210 highway corridor in Los Angeles (see Figure \ref{fig:small-network}) in the following scenarios
\begin{itemize}
\item \textit{Urban sprawl} ($N=300$): We emulate a city network where the density of cell towers is sufficient for recovering route flow in the noiseless setting.
\item \textit{City Center} ($N=375$): We emulate a popular commercial district with a dense sampling of cellular towers.
\end{itemize}
